Observed vs. Simulated Year Comparison

### 2022-01-11 03-post-process/compare-sim-to-obs.Rmd
Add ability to render the sim vs. obs output Rmd automatically
Just like for the standard output-plots.Rmd

# extract the two key structures from this object
# post = model_info$post                               # full posterior takes a long time to run on this script
post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
jags_data = model_info$jags_data
```

>>>>

# extract the two key structures from this object
post = model_info$post                               # full posterior takes a long time to run on this script
# post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
jags_data = model_info$jags_data
```
